---
title: API Usage
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{API Usage}
  %\VignetteEngine{litedown::vignette}
  %\VignetteEncoding{UTF-8}
---

```{r knitr-setup, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#"
)
```

## Storr setup

Create a `storr` either via `storr_tiledb()`:

```{r}
uri <- tempfile()
sto <- storr_tiledb(uri, init = TRUE)
```

Or more explicitly:

```{r}
uri2 <- tempfile()
dr <- driver_tiledb(uri2, init = TRUE)
sto2 <- storr::storr(dr)
```

The first approach generates a `TileDBStorr` object that represents the storr interface optimised for TileDB storage and provides additional functionality.
The latter is the standard `storr` object.

## API Usage

### 1. get, set, del
```{r}
dat <- head(mtcars, 2)

# set
sto$set("a", dat)
sto$set("b", list(name = "John"))
sto$mset(c("a", "b", "c"), value = list(dat, dat, dat), namespace = "ns1")

# get
sto$get("b")
sto$mget(c("b", "b"), namespace = c("objects", "ns1"))

# list keys
sto$list("objects")
sto$list("ns1")

# list namespaces
sto$list_namespaces()

# list hashes
sto$list_hashes()

# del
sto$del("a")
sto$del("b")
sto$exists("a")

# Retrieve hashes and namespaces
sto$list_namespaces()
sto$list_hashes()

# Delete unused hash
sto$gc()
sto$list_hashes()

# Delete by namespace
sto$clear("ns1")
sto$list("ns1")

```

### 2. get_keymeta, set_keymeta

With a key-namespace pair, you can attached notes and expiration metadata.

Set key metadata when creating a key:

```{r}
# Expires in 5 minutes
sto$set("aa", 1, expires_at = Sys.time() + 60 * 5, 
        notes = "{\"name\":\"John\",\"id\":12345}")

# Expires in 1 second
sto$set("bb", 1, expires_at = Sys.time() + 1)
```

Or update/retrieve with `$set_keymeta()` and `$get_keymeta()` methods:

```r
# Retrieve key metadata
sto$get_keymeta("aa", use_cache = FALSE)
sto$mget_keymeta(c("aa", "bb"), use_cache = TRUE)

# Update key metadata
sto$set_keymeta("bb", notes = "Updated Note")
sto$get_keymeta("bb")

```

**Expiration management**
```{r}
# Retrieve keys with expiration
sto$keys_with_expiration()

Sys.sleep(1)

# Retrieve expired keys
sto$expired_keys()

# Remove expired keys
sto$clear_expired_keys()

# Check for expired keys
sto$has_expired_keys()

# Or via gc()
sto$gc(clear_expired = TRUE)
```

**Clear metadata**
```{r}
sto$set_keymeta("aa", expires_at = as.POSIXct(NA), notes = NA_character_)
sto$get_keymeta("aa")
```


### 3. Async methods

Set keys without blocking R session:

```{r, eval=FALSE}
Sys.sleep(1)
sto$set_async("abc", 1)
sto$set_async("abc2", 2)
```



### 4. Fragments Management

When writing data to TileDB, it generates multiple array fragments on disk.
Over time, these files need to be consolidated in order to improve query
performance by reducing I/O overhead.

Note that the consolidation operation does **not** delete the old fragments;
it only creates new consolidated fragments. The actual cleanup of old fragments
is performed by the separate **vacuum** operation.

To manage storr TileDB fragments use `storr_fragments()` which encapsulates the 
consolidation and vacuum operations.

```{r }
# Set up a new storr
uri <- tempfile()
sto <- storr_tiledb(uri, init = TRUE)

# Set 3 keys and 2 objects
sto$set("a", 1)
sto$set("b", 2)
sto$set("c", 1)
```

```{r }
# Initialise StorrFragments class
fosto <- storr_fragments(uri)

# Total fragments (5, 3 for keys, 2 for hashes)
fosto$frag_num()

# Total fragments to vacuum
fosto$to_vacuum_num()
```

Consolidate everything (both arrays)

```{r }
# Consolidate all
fosto$consolidate()
```

```{r }
# Total fragments (2, 1 for keys, 1 for hashes)
fosto$frag_num()

# Total fragments to vacuum (5)
fosto$to_vacuum_num()
```
Now, let's clean up old fragments.

```{r }
# Cleaup old fragments
fosto$vacuum()

# Total fragments to vacuum (0)
fosto$to_vacuum_num()
```

```{r, echo=FALSE}
unlink(uri, recursive = TRUE)
unlink(uri2, recursive = TRUE)
```
