---
title: API Usage
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{API Usage}
  %\VignetteEngine{litedown::vignette}
  %\VignetteEncoding{UTF-8}
---

```{r knitr-setup, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#"
)
```

## Storr set up

Create a 'storr' using one of the two construction paths:

- use the specialised constructor `storr_tiledb()`:

```{r}
uri <- tempfile()
sto <- storr_tiledb(uri, init = TRUE)
```

- or explicitly with the standard 'storr' interface:

```{r}
uri2 <- tempfile()
dr <- driver_tiledb(uri2, init = TRUE)
sto2 <- storr::storr(dr)
```

Or, use the convenient wrapper when the driver is configured with one of `qs2` 
formats: 
```{r}
sto2 <- storr_tdb0(uri2)
```

The first approach generates a `TileDBStorr` object that represents the storr interface optimised for TileDB storage and provides additional functionality. The latter 
is the standard `storr` object.

For the rest of the vignette, the `storr_tiledb()` constructor will be used.

## API Examples

### 1. get, set, del
```{r}
dat <- head(mtcars, 2)

# set
sto$set("a", dat)
sto$set("b", list(name = "John"))
sto$mset(c("a", "b", "c"), value = list(dat, dat, dat), namespace = "ns1")

# get
sto$get("b")
sto$mget(c("b", "b"), namespace = c("objects", "ns1"))

# list keys
sto$list("objects")
sto$list("ns1")

# list namespaces
sto$list_namespaces()

# list hashes
sto$list_hashes()

# del
sto$del("a")
sto$del("b")
sto$exists("a")

# Retrieve hashes and namespaces
sto$list_namespaces()
sto$list_hashes()

# Delete unused hash
sto$gc()
sto$list_hashes()

# Delete by namespace
sto$clear("ns1")
sto$list("ns1")

```

### 2. get_keymeta, update_keymeta

With a key-namespace pair, you can attached notes and expiration metadata. Worth
noting that setting key-metadata will update/replace only the chosen metadata and
will not overwrite the other.

Set key metadata when creating a key:

```{r}
# Expires in 5 minutes
sto$set("aa", 1, expires_at = Sys.time() + 60 * 5, 
        notes = "{\"name\":\"John\",\"id\":12345}")

# Expires in 1 second
sto$set("bb", 1, expires_at = Sys.time() + 1)
```

Or update/retrieve with `$update_keymeta()` and `$get_keymeta()` methods:

```{r}
# Retrieve key metadata
sto$get_keymeta("aa", use_cache = FALSE)
sto$mget_keymeta(c("aa", "bb"), use_cache = TRUE)

# Update key metadata
sto$update_keymeta("bb", notes = "Updated Note")
sto$get_keymeta("bb")

```

Updating 'expires_at' metadata for key 'aa' will not overwrite 'notes'

```{r}
# Update 'expires_at'  
sto$update_keymeta("aa", expires_at = as.POSIXct(NA))

# Retains 'notes' value
sto$get_keymeta("aa")

```

**Fetch single metadata**

For getting only one metadata value, either expiration or notes, `storr.tiledb`
offers efficient methods:

```{r}
# Get only notes for key 'aa' 
sto$get_keymeta_notes("aa")

# # Get only expiration date-times 
sto$mget_keymeta_expires_at(c("aa", "bb"))
```

**Expiration management**
  
```{r}
# Retrieve keys with expiration
sto$keys_with_expiration()

Sys.sleep(1)

# Retrieve expired keys
sto$expired_keys()

# Remove expired keys
sto$clear_expired_keys()

# Check for expired keys
sto$has_expired_keys()

# Or via gc()
sto$gc(clear_expired = TRUE)
```

**Clear metadata**
```{r}
sto$clear_keymeta("aa")
sto$get_keymeta("aa")
```
### 3. update

Use `update()` and `mupdate()` to replace  key-values and retain their key-metadata.

```{r}
# Add new key
sto$set("mykey", 1, notes = "mykey")

# Update "mykey"
sto$update("mykey", 10)

# Check new value
sto$get("mykey")

# Check 'notes' metadata
sto$get_keymeta_notes("mykey")
```

### 4. Async methods

Set keys without blocking R session:

```{r, eval=FALSE}
Sys.sleep(1)
sto$set_async("abc", 1)
sto$set_async("abc2", 2)
```



### 5. Fragments Management

When writing data to TileDB, it generates multiple array fragments on disk.
Over time, these files need to be consolidated in order to improve query
performance by reducing I/O overhead.

Note that the consolidation operation does **not** delete the old fragments;
it only creates new consolidated fragments. The actual cleanup of old fragments
is performed by the separate **vacuum** operation.

To manage storr TileDB fragments use `storr_fragments()` which encapsulates the 
consolidation and vacuum operations.

```{r }
# Set up a new storr
uri <- tempfile()
sto <- storr_tiledb(uri, init = TRUE)

# Set 3 keys and 2 objects
sto$set("a", 1)
sto$set("b", 2)
sto$set("c", 1)
```

```{r }
# Initialise StorrFragments class
fosto <- storr_fragments(uri)

# Total fragments (5, 3 for keys, 2 for hashes)
fosto$frag_num()

# Total fragments to vacuum
fosto$to_vacuum_num()
```

Consolidate everything (both arrays)

```{r }
# Consolidate all
fosto$consolidate()
```

```{r }
# Total fragments (2, 1 for keys, 1 for hashes)
fosto$frag_num()

# Total fragments to vacuum (5)
fosto$to_vacuum_num()
```
Now, let's clean up the old fragments.

```{r }
# Cleaup old fragments
fosto$vacuum()

# Total fragments to vacuum (0)
fosto$to_vacuum_num()
```

```{r, echo=FALSE}
unlink(uri, recursive = TRUE)
unlink(uri2, recursive = TRUE)
```
