---
title: Storr Data Models
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Storr Data Models}
  %\VignetteEngine{litedown::vignette}
  %\VignetteEncoding{UTF-8}
---

```{r knitr-setup, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#"
)
```

## Overview

This vignette describes the **Content-Addressable Storage (CAS)** data model used by
the storr.tiledb driver. The driver stores storr data inside a TileDB Group that contains
two Sparse Arrays:

- `tbl_keys` maps key-namespace pairs to hashes and optional key metadata
- `tbl_data` maps content hashes to serialized object values

The arrays are stored as members inside a TileDB Group at the driver's URI. The Group also contains metadata about the storage format.

---

## CAS: Group Structure

### Members

1. `tbl_keys` (array) maps key/namespace pairs to hashes and can store expiry and notes.
2. `tbl_data` (array) maps content hashes to serialized R objects.

### Metadata

 - `hash_algo` - name of the hash algorithm used (e.g., `"sha256"`).
 - `type` - group identifier string `"storr"`.
 - `serial_format` - name of the serialization format used (e.g., `"rds"`).

---

## Array data models

### **`tbl_keys`** array 

A 2-dimensional sparse array that maps key-namespace pairs to hashes and key-metadata.

**Dimensions** 

  - `namespace` (*ASCII*) 
  - `key` (*ASCII*)
  
**Attributes**

  - `hash` (*ASCII*)
  - `expires_at` (*DATETIME_MS*)
  - `notes` (*UTF8*)


### **`tbl_data`** array 

A 1-dimensional sparse array that maps content hashes to serialized values.

**Dimensions**

 - `hash` (*ASCII*)
 
**Attributes** 

 - `value` (*ASCII*)

TileDB datatypes shown in parentheses.

### Example

Below is a short example that shows creating a TileDB-backed driver and inspecting its layout.

```{r}
# Create a temporary URI
uri <- tempfile()

# Create a driver (initializes the TileDB Group and member arrays)
dr <- driver_tiledb(uri, init = TRUE)
```

Inspecting the driver directory tree:
```{r, collapse=FALSE}

dr$dir_tree()
```

