---
title: Data Model
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Data Model}
  %\VignetteEngine{litedown::vignette}
  %\VignetteEncoding{UTF-8}
---

```{r knitr-setup, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#"
)
```

## Overview

The **Content Addressable Storage (CAS)** system using TileDB as the underlying 
storage consists of collection two Sparse Arrays: one that maps keys to hashes
and another that maps hashes to objects.

Specifically, the driver storage is a TileDB Group with two member TileDB Arrays
which are stored relative to Group's URI path.

## CAS 

### Group Structure

**`Members`**

1. `tbl_keys` (array): maps key-namespace pairs to hashes (and to expiry and/or
notes, optional)
2. `tbl_data` (array): maps hashes to values (serialised R objects)

**`Metadata`**

 - `hash_algo`: The name of hash algorithm.
 - `type`: Group identifier, `"storr"`

### Array Data Models

**`tbl_keys`** - A 2D sparse array that maps key-namespace pairs to hashes and key-metadata.

 - **Dimensions**: `namespace` (*ASCII*) and `key` (*ASCII*)
 - **Attributes**: `hash` (*ASCII*), `expires_at` (*DATETIME_MS*) and `notes` (*UTF8*)


**`tbl_data`** - A 1D sparse array that maps hashes to object values.

 - **Dimensions**: `hash` (*ASCII*)
 - **Attributes**: `value` (*ASCII*)

 TileDB datatypes in parentheses.

### Example

```{r}
# URI path
uri <- tempfile()

# Create a driver
dr <- driver_tiledb(uri, init = TRUE)
```

CAS Structure:
```{r, collapse=FALSE}

dr$dir_tree()
```

