---
title: FAQ
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{FAQ}
  %\VignetteEngine{litedown::vignette}
  %\VignetteEncoding{UTF-8}
---



```{r knitr-setup, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#"
)
```

**storr.tiledb FAQ**

***


####  Can I change the storr's hash algorithm?
  
Yes, by using driver's active field `$hash_algorithm`:

```{r}
# URI path
uri <- tempfile()

# Create a storr with "sha256" digest
sto <- storr_tiledb(uri, init = TRUE, hash_algorithm = "sha256")

sto$set("a", 1)

sto$get_hash("a")
```

Change the hash algorithm as follows:
```{r}
# Initialise the driver
dr <- driver_tiledb(uri)

# Check its hash algo
dr$hash_algorithm

# Change hash digest to 'md5'
dr$hash_algorithm <- 'md5'

dr$hash_algorithm
```

Reopen storr to pick up the new hash algorithm:

```{r}
# Open new storr instance
sto <- storr_tiledb(uri)

sto$set("a", 1)

# key 'a' is hashed with 'md5'
sto$get_hash("a")

```

####  How can I rehash the entire key-value storr?

You need to create a new storr with the desired hash algorithm,
and then export from source storr to the new one.

```{r}
# source storr
uri <- tempfile()
sto <- storr_tiledb(uri, init = TRUE)
sto$set("a", 1)
sto$get_hash("a")
```

```{r}
# create a storr with new hash algorithm
uri_dest <- tempfile()
sto_dest <- storr_tiledb(uri_dest, init = TRUE, hash_algorithm = "blake3")
```

Now, export from source to destination storr using the class method
`$export_tdb()`:
```{r}
sto$export_tdb(uri_dest = uri_dest)

# check
sto_dest$set("a", 1)
sto_dest$get_hash("a")
```

