---
title: Quick Reference
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Quick Reference}
  %\VignetteEngine{litedown::vignette}
  %\VignetteEncoding{UTF-8}
---

```{r knitr-setup, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#"
)
```


## Overview

 **storr**: a key value store interface provided by homonymous R package.
 For its implementation details, please refer to [storr](https://richfitz.github.io/storr/articles/storr.html) vignette.
 
 **storr_tiledb**: a function that implements the storr interface with TileDB backend.

## 1. Basic Usage

### Create a TileDB Storr

```{r}
# URI path
uri <- tempfile()
# Create a new storr with TileDB driver
sto <- storr_tiledb(uri, init = TRUE)
```

Alternatively, you can use `driver_tiledb_create()` for the side-effects and then instantiate
a TileDB Storr for the given URI path as follows:

```{r}
# Clean up previous path
unlink(uri, recursive = TRUE)

# URI path
uri <- tempfile()

# Create driver
driver_tiledb_create(uri)

# Open storr
sto <- storr_tiledb(uri)
```

### set(), get()

```{r}
sto$set("a", head(mtcars, 2))
sto$mset(c("b", "c"), list(head(mtcars, 2), 1))

# list keys for the default namespace
sto$list()

sto$get("a")
```

### Deduplication

We saved three keys, but only two `R` objects. Check for deduplication:
```{r}
# 2 hashes for 3 keys
hashes <- sto$list_hashes()
hashes

# get R object for this hash
sto$get_value(hashes[1])
```

### del(), gc() and listing methods

```{r}
sto$del(c("b", "c"))

# Not found
sto$get("b")

# NB: none object has been deleted, only the index
sto$list_hashes()

# Now, delete the unused hashes
sto$gc()

# Only one hash is left
sto$list_hashes()
```
## 2. Key Metadata

With `storr_tiledb()`, we can add notes and/or expiration timestamps to
key-namespace pairs.

```{r}
# This key will expire momentarily!
sto$set("key1", 10, notes = "my notes", expires_at = Sys.time() + 1)
sto$set("key2", 10, expires_at = as.POSIXct(Sys.time() + 100))

# Retrieve 'notes' and 'expiration'
sto$get_keymeta("key1")
```

### Expiration Management

```{r}
# Get keys with expiration time-stamp
sto$keys_with_expiration()

Sys.sleep(2)

sto$has_expired_keys()

sto$expired_keys()

sto$clear_expired_keys()

# Also, you can clear expired keys with gc()
sto$gc(clear_expired = TRUE)

sto$has_expired_keys()
sto$expired_keys()

# Get keys with expiration time-stamp
sto$keys_with_expiration()

# Reset expiration timestamp
sto$set_keymeta("key2", expires_at = as.POSIXct(NA))

# No key with expiration time-stamp
sto$keys_with_expiration()
```

## 3. Async methods

`storr_tiledb()` supports storing keys in asynchronous or in parallel
via `mirai` framework.

```{r}
# Set asynchronously (non-blocking)
sto$set_async("key3", 2, namespace = "_session")
sto$set_async("key1", 1, namespace = "ns1")
sto$set_keymeta_async("key2", notes = "key1-note")

Sys.sleep(0.5)

# Retrieve key, keymeta
sto$get("key3", "_session")
sto$get_keymeta("key2", "objects")

```


```{r}
# clear default namespace
sto$clear()

# set keys in parallel
vals <- 1:3
keys <- paste0("aa", vals)

ma <- mapply(function(k, v) {

  sto$set_async(k,
                value = v,
                use_cache = FALSE)
  },
  k = keys, v = vals, SIMPLIFY = FALSE)


Sys.sleep(2)

sto$index_export(namespace = "objects")[, 1:3]

```


## 4. Encrypted Storr

TileDB backend supports encryption:

```{r}
# Requires a TileDB Context with encryption configuration parameters
key <- "5b643a5e173c27d76b3f2af01fcb327b"
config <- tiledb::tiledb_config()
config["sm.encryption_type"] <- "AES_256_GCM";
config["sm.encryption_key"] <- key
ctx <- R6.tiledb::new_context(config) # tiledb::tiledb_ctx(config)
```

Note that we've created a context using `R6.tiledb::new_context()` instead of `tiledb_tiledb_ctx()`, because the latter stores the context to package cache.

Now, create a storr with encryption:

```{r}
# Create a storr with context that encapsulates encryption configuration
uri_enc <- tempfile()
stoe <- storr_tiledb(uri_enc, init = TRUE, context = ctx)

stoe$set("a", 1)
stoe$get("a") 

# No access without the key
stoe_new <- storr_tiledb(uri_enc)

# Pass the context with encryption parameters
stoe_new <- storr_tiledb(uri_enc, context = ctx)
stoe_new$get("a")
```

## 5. Remote Storr

Create a storr in cloud storage:
```{r, eval=FALSE}
# Set context with AWS S3 config parameters
# NB: store values in ENV or in credential store, i.e., via keyring package
config <- tiledb::tiledb_config()

config["vfs.s3.region"] <- Sys.getenv("AWS_DEFAULT_REGION")
config["vfs.s3.aws_access_key_id"] <- Sys.getenv("AWS_ACCESS_KEY_ID")
config["vfs.s3.aws_secret_access_key"] <- Sys.getenv("AWS_SECRET_ACCESS_KEY")
ctx <- R6.tiledb::new_context(config)
```

```{r, eval=FALSE}
# Create a remote storr
uri <- 's3//bucket/my-storr'
sto <- storr_tiledb(uri, init = TRUE, context = ctx)
```



```{r, echo=FALSE}
unlink(uri, recursive = TRUE)
```
