---
title: Time Travelling
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Time Travelling}
  %\VignetteEngine{litedown::vignette}
  %\VignetteEncoding{UTF-8}
---

```{r knitr-setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#"
)
```

## Overview

This vignette demonstrates the time-travel capabilities provided by storr.tiledb via
`storr_timetravel()` and the `TimeTravelDriver`/`StorrTimeTravel` classes. Use time-travel
to open a storr at a specific TileDB timestamp range (read-only) and inspect the state
of keys and objects at that time.

### 1. Create a storr and write values at successive times

```{r}
# Create a storr
uri <- tempfile()
sto <- storr_tiledb(uri, init = TRUE, default_namespace = "ns1")

# Record timestamps around operations
t0 <- Sys.time()
sto$set("a", 1)   # first version of "a"
t1 <- Sys.time()
sto$set("a", 2)   # updated "a"
sto$set("b", 3, namespace = "ns2")
t2 <- Sys.time()

# Verify current (latest) state
sto$list()
sto$list_hashes()
sto$get("a")
sto$get("b", namespace = "ns2")
```

### 2. Open a time-travel storr at t0 (before any writes)

```{r}
stor <- storr_timetravel(uri, default_namespace = "ns1", timestamp = t0)

# At t0 nothing should be present
stor$list()
stor$list_hashes()
# Attempting to read keys written after t0 should error
stor$get("a")

```

### 3. Move forward to t1 and inspect the state

```{r}
# Set the timestamp to t1 (this uses the active binding)
stor$timestamp <- t1

# At t1 "a" has the first value, "b" is not yet present in ns2
stor$list()
stor$get("a")
stor$mget(c("a", "b"), namespace = c("ns1", "ns2"))
stor$exists(c("a", "b"), namespace = c("ns1", "ns2"))
```

### 4. Move forward to t2 and inspect the later state

```{r}
stor$timestamp <- t2

# Now "a" has the updated value and "b" exists in ns2 (but default_namespace is ns1)
stor$get("a")
# mget across namespaces
stor$mget(c("a", "b"), namespace = c("ns1", "ns2"))
stor$list_namespaces()
stor$list_hashes()
```

### 5. Read-only behaviour

`StorrTimeTravel` is designed for read-only access. Attempts to modify the store via
the time-travel object should fail:

```{r}
# Try writing — should error
stor$set("z", 10)
```

### 6. Using timestamp ranges

You can also open a time-travel storr with an explicit start/end timestamp pair to
see the state as of the end timestamp (and the tileDB timestamp object can be created
with `set_tiledb_timestamp()` when needed). Example below demonstrates the idea:

```{r}
# Example: create a timestamp range (end only here)
stor$timestamp <- t1          # open at t1 (end)
stor$get("a")                # retrieves version at or before t1

# If you need an explicit tiledb_timestamp object:
# tt <- set_tiledb_timestamp(Sys.time() - 3600, Sys.time())
# stor$timestamp <- tt
```

### 7. Reset timestamp to present

Set timestamp field to `NULL` to reset storr state to present. 

```{r}
# Set the timestamp to present 
stor$timestamp <- NULL
stor$mget(c("a", "b"), namespace = c("ns1", "ns2"))

```
## Notes

- Time-travel storrs reuse the underlying TileDB fragments, and the `timestamp` active
  binding controls the time-range used when opening/reading the arrays.
- Because time-travel is read-only, consider using a regular `storr_tiledb()` for
  writes and `storr_timetravel()` for inspections of historical states.
  
## References

- [`storr_timetravel()`](https://cgiachalis.github.io/storr.tiledb/reference/storr_timetravel.html)
- [R6.tiledb - Time Travelling](https://cgiachalis.github.io/R6.tiledb/articles/timetravel.html)
